Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 supplement.tex
More tweaking the sections 2 to 4
add list dataset to supplement

\begin{wrapfigure}{L}{0.5\textwidth}
  \begin{minipage}{0.49\textwidth}    
\begin{algorithm}[H]
   \caption{Generative model over programs}
   \label{programGenerativeModel}
   \begin{algorithmic}
%%      \STATE \textbf{function} sampleProgramFromDSL$(\mathcal{D}, \theta, \tau)$:
%%   \STATE {\bfseries Input:} DSL $\mathcal{D}$, weight vector $\theta$, type $\tau$
%%   \STATE \textbf{Output:} a program whose type unifies with $\tau$
%%   \STATE \textbf{return} sample$(\mathcal{D}, \theta, \varnothing, \tau)$
%% \STATE
     \STATE \textbf{function} sample$(\mathcal{D}, \theta, \mathcal{E}, \tau)$:
  \STATE {\bfseries Input:} DSL $(\mathcal{D},\theta)$, environment $\mathcal{E}$, type $\tau$
  \STATE \textbf{Output:} a program whose type unifies with $\tau$
  \IF{$\tau = \alpha\to\beta$}
  \STATE var $\gets$ an unused variable name
  \STATE body $\sim$ sample$(\mathcal{D},\theta,\{\text{var}:\alpha\}\cup\mathcal{E},\beta)$
   \STATE \textbf{return} \code{(lambda (}var\code{) }body\code{)}
   \ENDIF
   %   \ELSE
   \STATE $\text{primitives} \gets\{p | p: \tau' \in \mathcal{D}\cup\mathcal{E}$ \\
      \hspace*{6.9em}$\text{if }\tau\text{ can unify with yield}(\tau') \} $

   \STATE Draw $e\sim \text{primitives}$, w.p. $\propto\theta_e$ if $e\in \mathcal{D}$ \\
      \hspace*{8.8em}w.p. $\propto\frac{\theta_{var}}{|\text{variables}|}$ if $e\in \mathcal{E}$
   \STATE Unify $\tau$ with yield$(\tau')$.
   \STATE $\left\{\alpha_k \right\}_{k = 1}^K\gets\text{args}(\tau')$ 
%   \STATE unify$(\tau,\beta)$
   \FOR{$k=1$ {\bfseries to} $K$}
 \STATE $a_k\sim\text{sample}(\mathcal{D},\theta,\mathcal{E},\alpha_k)$
 \ENDFOR
 \STATE \textbf{return} \code{(}$e\;a_1\; a_2\; \cdots\; a_K$\code{)}
 \STATE\textbf{where:}
 \STATE yield$(\tau) = \begin{cases}
   \text{yield}(\beta)   &\text{ if }\tau = \alpha\to \beta\\
   \tau   &\text{ otherwise.}
 \end{cases}$ 
 \STATE  args$(\tau) = \begin{cases}
   [\alpha] + \text{args}(\beta)   &\text{ if }\tau = \alpha\to \beta\\
   []   &\text{ otherwise.}
 \end{cases}$
\end{algorithmic}
\end{algorithm}
    \end{minipage}
  \end{wrapfigure}

@@

@@

\pagebreak
\onecolumn
\subsection{Symbolic regression}
\begin{lstlisting}
#(\ (#(\ (+. $0 REAL)) (*. $0 REAL)))
#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0)))
#(\ (#(\ (+. $0 REAL)) (*. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) $0)))
#(\ (#(/. REAL) (#(\ (+. $0 REAL)) $0)))
#(/. REAL)
#(\ (/. (/. REAL $0) $0))
#(\ (+. $0 REAL))
#(\ (#(\ (+. $0 REAL)) (*. $0 (#(\ (#(\ (+. $0 REAL)) (*. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) $0))) $0))))
#(\ (/. (#(\ (/. (/. REAL $0) $0)) $0) $0))
#(\ (\ (#(/. REAL) (/. (#(\ (+. $0 REAL)) $0) $1))))
#(\ (#(\ (+. $0 REAL)) (#(\ (#(/. REAL) (#(\ (+. $0 REAL)) $0))) $0)))
#(#(\ (\ (#(/. REAL) (/. (#(\ (+. $0 REAL)) $0) $1)))) (#(\ (/. (#(\ (/. (/. REAL $0) $0)) $0) $0)) REAL))
#(\ (/. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) (#(\ (+. $0 REAL)) $0)))
\end{lstlisting}

\subsection{String editing}
\begin{lstlisting}
#(\ (\ (fold $0 $0 (\ (\ (if (char-eq? $1 $3) empty (cons $1 $0)))))))
#(\ (\ (fold $0 $1 (\ (\ (cons $1 $0))))))
#(\ (\ (fold $0 $0 (\ (\ (cdr (if (char-eq? $1 $3) $2 $0)))))))
#(\ (\ (#(\ (\ (fold $0 $1 (\ (\ (cons $1 $0)))))) (cons $0 $1))))
#(\ (\ (fold $0 $0 (\ (\ (fold $0 $0 (\ (\ (if (char-eq? $1 $5) (cdr $2) $0)))))))))
#(\ (#(\ (\ (\ (cons (car $0) (cons $1 $2))))) (#(#(\ (\ (\ (cons (car $0) (cons $1 $2))))) empty) '.' $0) '.'))
#(\ (\ (map (\ (if (char-eq? $1 $0) $2 $0)))))
#(\ (map (\ (index $0 $1))))
#(\ (unfold $0 (\ (empty? $0)) (\ (car $0)) (\ (#(\ (\ (fold $0 $0 (\ (\ (cdr (if (char-eq? $1 $3) $2 $0))))))) SPACE $0))))
#(#(\ (\ (\ (cons (car $0) (cons $1 $2))))) empty)
\end{lstlisting}

@@

>>>>

\begin{figure}
  \centering
  \begin{minipage}{0.5\textwidth}    
    \begin{algorithm}[H]
       \caption{Generative model over programs}
       \label{programGenerativeModel}
       \begin{algorithmic}
    %%      \STATE \textbf{function} sampleProgramFromDSL$(\mathcal{D}, \theta, \tau)$:
    %%   \STATE {\bfseries Input:} DSL $\mathcal{D}$, weight vector $\theta$, type $\tau$
    %%   \STATE \textbf{Output:} a program whose type unifies with $\tau$
    %%   \STATE \textbf{return} sample$(\mathcal{D}, \theta, \varnothing, \tau)$
    %% \STATE
         \STATE \textbf{function} sample$(\mathcal{D}, \theta, \mathcal{E}, \tau)$:
      \STATE {\bfseries Input:} DSL $(\mathcal{D},\theta)$, environment $\mathcal{E}$, type $\tau$
      \STATE \textbf{Output:} a program whose type unifies with $\tau$
      \IF{$\tau = \alpha\to\beta$}
      \STATE var $\gets$ an unused variable name
      \STATE body $\sim$ sample$(\mathcal{D},\theta,\{\text{var}:\alpha\}\cup\mathcal{E},\beta)$
       \STATE \textbf{return} \code{(lambda (}var\code{) }body\code{)}
       \ENDIF
       %   \ELSE
       \STATE $\text{primitives} \gets\{p | p: \tau' \in \mathcal{D}\cup\mathcal{E}$ \\
          \hspace*{6.9em}$\text{if }\tau\text{ can unify with yield}(\tau') \} $

       \STATE Draw $e\sim \text{primitives}$, w.p. $\propto\theta_e$ if $e\in \mathcal{D}$ \\
          \hspace*{8.8em}w.p. $\propto\frac{\theta_{var}}{|\text{variables}|}$ if $e\in \mathcal{E}$
       \STATE Unify $\tau$ with yield$(\tau')$.
       \STATE $\left\{\alpha_k \right\}_{k = 1}^K\gets\text{args}(\tau')$ 
    %   \STATE unify$(\tau,\beta)$
       \FOR{$k=1$ {\bfseries to} $K$}
     \STATE $a_k\sim\text{sample}(\mathcal{D},\theta,\mathcal{E},\alpha_k)$
     \ENDFOR
     \STATE \textbf{return} \code{(}$e\;a_1\; a_2\; \cdots\; a_K$\code{)}
     \STATE\textbf{where:}
     \STATE yield$(\tau) = \begin{cases}
       \text{yield}(\beta)   &\text{ if }\tau = \alpha\to \beta\\
       \tau   &\text{ otherwise.}
     \end{cases}$ 
     \STATE  args$(\tau) = \begin{cases}
       [\alpha] + \text{args}(\beta)   &\text{ if }\tau = \alpha\to \beta\\
       []   &\text{ otherwise.}
     \end{cases}$
    \end{algorithmic}
    \end{algorithm}
  \end{minipage}
\end{figure}

@@

\section{List Processing Data Set}
Each list processing tasks we created is in described in
Tbl~\ref{listdataset}.

\begin{table}[h]
  \centering\footnotesize
  \begin{tabular}{|l|l|}\hline
    add-k for k $\in\{0..5\}$&
kth-largest for k $\in\{1..5\}$\\
    append-index-k for k $\in\{1..5\}$&
kth-smallest for k $\in\{1..5\}$\\
    append-k for k $\in\{0..5\}$&
last\\
    bool-identify-geq-k for k $\in\{0..5\}$&
len\\
    bool-identify-is-mod-k for k $\in\{1..5\}$&
max\\
    bool-identify-is-prime&
min\\
    bool-identify-k for k $\in\{0..5\}$&
modulo-k for k $\in\{1..5\}$\\
    caesar-cipher-k-modulo-n&
mult-k for k $\in\{0..5\}$\\
    \qquad for k $\in\{0..5\}$ and n $\in\{1..5\}$&
odds\\
    count-head-in-tail&
pop\\
    count-k for k $\in\{0..5\}$&
pow-k for k $\in\{1..5\}$\\
    drop-k for k $\in\{0..5\}$&
prepend-index-k for k $\in\{1..5\}$\\
    dup&
prepend-k for k $\in\{0..5\}$\\
    empty&
product\\
    evens&
range\\
    fibonacci&
remove-empty-lists\\
    has-head-in-tail&
remove-eq-k for k $\in\{0..3\}$\\
    has-k for k $\in\{0..5\}$&
remove-gt-k for k $\in\{0..3\}$\\
    head&
remove-index-k for k $\in\{1..5\}$\\
    index-head&
remove-mod-head\\
    index-k for k $\in\{1..5\}$&
remove-mod-k for k $\in\{2..5\}$\\
    is-evens&
repeat\\
    is-mod-k for k $\in\{1..5\}$&
repeat-k for k $\in\{1..5\}$\\
    is-odds&
repeat-many\\
    is-primes&
replace-all-with-index-k for k $\in\{1..5\}$\\
    is-squares&
reverse\\
    keep-eq-k for k $\in\{0..3\}$&
rotate-k for k $\in\{1..5\}$\\
    keep-gt-k for k $\in\{0..3\}$&
slice-k-n for k $\in\{1..5\}$ and n $\in\{1..5\}$\\
    keep-mod-head&
sort\\
    keep-mod-k for k $\in\{1..5\}$&
sum\\
    keep-primes&
tail\\
    keep-squares&
take-k for k $\in\{1..5\}$\\
\hline
  \end{tabular}
  \normalsize
  ~\\~\\\caption{Our list processing data set}\label{listdataset}
\end{table}

@@

\pagebreak
\onecolumn

@@

\subsection{Text editing}
\begin{lstlisting}
#(\ (\ (fold $0 $0 (\ (\ (if (char-eq? $1 $3) empty (cons $1 $0)))))))
#(\ (\ (fold $0 $1 (\ (\ (cons $1 $0))))))
#(\ (\ (fold $0 $0 (\ (\ (cdr (if (char-eq? $1 $3) $2 $0)))))))
#(\ (\ (#(\ (\ (fold $0 $1 (\ (\ (cons $1 $0)))))) (cons $0 $1))))
#(\ (\ (fold $0 $0 (\ (\ (fold $0 $0 (\ (\ (if (char-eq? $1 $5) (cdr $2) $0)))))))))
#(\ (#(\ (\ (\ (cons (car $0) (cons $1 $2))))) (#(#(\ (\ (\ (cons (car $0) (cons $1 $2))))) empty) '.' $0) '.'))
#(\ (\ (map (\ (if (char-eq? $1 $0) $2 $0)))))
#(\ (map (\ (index $0 $1))))
#(\ (unfold $0 (\ (empty? $0)) (\ (car $0)) (\ (#(\ (\ (fold $0 $0 (\ (\ (cdr (if (char-eq? $1 $3) $2 $0))))))) SPACE $0))))
#(#(\ (\ (\ (cons (car $0) (cons $1 $2))))) empty)
\end{lstlisting}

\subsection{Symbolic regression}
\begin{lstlisting}
#(\ (#(\ (+. $0 REAL)) (*. $0 REAL)))
#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0)))
#(\ (#(\ (+. $0 REAL)) (*. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) $0)))
#(\ (#(/. REAL) (#(\ (+. $0 REAL)) $0)))
#(/. REAL)
#(\ (/. (/. REAL $0) $0))
#(\ (+. $0 REAL))
#(\ (#(\ (+. $0 REAL)) (*. $0 (#(\ (#(\ (+. $0 REAL)) (*. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) $0))) $0))))
#(\ (/. (#(\ (/. (/. REAL $0) $0)) $0) $0))
#(\ (\ (#(/. REAL) (/. (#(\ (+. $0 REAL)) $0) $1))))
#(\ (#(\ (+. $0 REAL)) (#(\ (#(/. REAL) (#(\ (+. $0 REAL)) $0))) $0)))
#(#(\ (\ (#(/. REAL) (/. (#(\ (+. $0 REAL)) $0) $1)))) (#(\ (/. (#(\ (/. (/. REAL $0) $0)) $0) $0)) REAL))
#(\ (/. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) (#(\ (+. $0 REAL)) $0)))
\end{lstlisting}
